geojson
=======

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![cran checks](https://cranchecks.info/badges/worst/geojson)](https://cranchecks.info/pkgs/geojson)
[![Build Status](https://travis-ci.org/ropensci/geojson.svg?branch=master)](https://travis-ci.org/ropensci/geojson)
[![codecov](https://codecov.io/gh/ropensci/geojson/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/geojson)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/geojson)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/geojson)](https://cran.r-project.org/package=geojson)

`geojson` aims to deal only with geojson data, without requiring any of the
`sp`/`rgdal`/`rgeos` stack.  That means this package is light weight.

We've defined classes (`S3`) following the [GeoJSON spec][geojsonspec]. These
classes sort of overlap with `sp`'s classes, but not really. There's also some
overlap in GeoJSON classes with Well-Known Text (WKT) classes, but GeoJSON has a
subset of WKT's classes.

The package [geoops](https://github.com/ropenscilabs/geoops) supports manipulations on
the classes defined in this package. This package is used within
[geojsonio](https://github.com/ropensci/geojsonio) to make some tasks easier.

## Installation

Stable CRAN version

`````{r eval=FALSE}
install.packages("geojson")
```

Dev version

```{r eval=FALSE}
devtools::install_github("ropensci/geojson")
```

```{r}
library("geojson")
```

## geojson class

Essentially a character string with S3 class `geojson` attached to make it
easy to perform operations on

```{r}
x <- "{\"type\":\"FeatureCollection\",\"features\":[{\"type\":\"Feature\",\"geometry\":{\"type\":\"Point\",\"coordinates\":[-99.74,32.45]},\"properties\":{}}]}"
as.geojson(x)
```

## geometrycollection

```{r}
x <- '{
 "type": "GeometryCollection",
 "geometries": [
   {
     "type": "Point",
     "coordinates": [100.0, 0.0]
   },
   {
     "type": "LineString",
     "coordinates": [ [101.0, 0.0], [102.0, 1.0] ]
   }
  ]
}'
(y <- geometrycollection(x))
```

### inspect the object

get the string

```{r}
y[[1]]
```

get the type

```{r}
geo_type(y)
```

pretty print the geojson

```{r}
geo_pretty(y)
```

write to disk

```{r}
geo_write(y, f <- tempfile(fileext = ".geojson"))
jsonlite::fromJSON(f, FALSE)
```

```{r echo=FALSE}
unlink(f)
```

## properties

Add properties

```{r}
x <- '{ "type": "LineString", "coordinates": [ [100.0, 0.0], [101.0, 1.0] ]}'
res <- linestring(x) %>% feature() %>% properties_add(population = 1000)
res
```

Get a property

```{r}
properties_get(res, property = 'population')
```

## crs

Add crs

```{r}
crs <- '{
  "type": "name",
  "properties": {
     "name": "urn:ogc:def:crs:OGC:1.3:CRS84"
  }
}'
z <- x %>% feature() %>% crs_add(crs)
z
```

Get crs

```{r}
crs_get(z)
```

## bbox

Add bbox

```{r}
tt <- x %>% feature() %>% bbox_add()
tt
```

Get bbox

```{r}
bbox_get(tt)
```


## geojson in data.frame's

```{r}
x <- '{ "type": "Point", "coordinates": [100.0, 0.0] }'
(pt <- point(x))
```

```{r}
library("tibble")
data_frame(a = 1:5, b = list(pt))
```

```{r}
x <- '{ "type": "MultiLineString",
  "coordinates": [ [ [100.0, 0.0], [101.0, 1.0] ], [ [102.0, 2.0], [103.0, 3.0] ] ] }'
(mls <- multilinestring(x))
```

```{r}
data_frame(a = 1:5, b = list(mls))
```

```{r}
data_frame(a = 1:5, b = list(pt), c = list(mls))
```


## Meta

* Please [report any issues or bugs](https://github.com/ropensci/geojson/issues).
* License: MIT
* Get citation information for `geojson` in R doing `citation(package = 'geojson')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.


[geojsonspec]: https://tools.ietf.org/html/rfc7946
[jqr]: https://github.com/ropensci/jqr
[jq]: https://github.com/stedolan/jq
