geojson
=======

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

`geojson` aims to deal only with geojson data, without requiring any of the `sp`/`rgdal`/`rgeos` stack. That means this package can be relatively light weight.

We'll define classes (`S3` or `R6`) following the [GeoJSON spec][geojsonspec]. These classes sort of overlap with `sp`'s classes, but not really. There's also some overlap in GeoJSON classes with Well-Known Text (WKT) classes, but GeoJSON has a subset of WKT's classes.

[geoops](https://github.com/ropenscilabs/geoops) supports manipulations on these classes.

## installation

```{r eval=FALSE}
devtools::install_github("ropenscilabs/geojson")
```

```{r}
library("geojson")
```

## geojson class

this is just a characstring string with S3 class `geojson` attached to make it easy to perform operations on

```{r}
x <- "{\"type\":\"FeatureCollection\",\"features\":[{\"type\":\"Feature\",\"geometry\":{\"type\":\"Point\",\"coordinates\":[-99.74,32.45]},\"properties\":{}}]}"
as.geojson(x)
```

## Playing with using R6

```{r}
x <- '{
 "type": "GeometryCollection",
 "geometries": [
   {
     "type": "Point",
     "coordinates": [100.0, 0.0]
   },
   {
     "type": "LineString",
     "coordinates": [ [101.0, 0.0], [102.0, 1.0] ]
   }
  ]
}'
(y <- geometrycollection(x))
```

creates an object which we can use to inspect the geojson

```{r}
# get the string
y$string
# get the type
y$type()
# pretty print the geojson
y$pretty()
# get the types within the geometrycollection
y$types()
# write to disk
y$write(file = (f <- tempfile(fileext = ".geojson")))
unlink(f)
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/sifter/issues).
* License: MIT

[geojsonspec]: http://geojson.org/geojson-spec.html
[jqr]: https://github.com/ropensci/jqr
[jq]: https://github.com/stedolan/jq
